---
title: "Data Analysis "
author: "Jannik Möllmann"
date: "`r Sys.Date()`"
output: html_document
---

## Libraries
```{r, message=F}

library(tidyverse)
library(lme4)
library(mgcv)
library(emmeans)
library(Rmisc)
library(ggtext)
library(modelr)
library(patchwork)
```


## Custom Color Palettes
```{r}
customPalette1 <- c("#EDE100", "#E69F00", "#D55E00")
customPalette2 <- c("#11B989", "#14701D", "#F0266A", "#B20980")
```

## Load data
```{r}
raw_data <- read_tsv("supplementary_tables/1_raw_data.tsv")
temp_logger_data <- read_tsv("supplementary_tables/2_temp_logger_data.tsv")
```

## Error corrections and outlier removal
```{r, warning = F}
error_plot_1 <- raw_data %>% 
  dplyr::filter(emergence_status %in% c("emerged", "excised"), !is.na(emergence_condition)) %>% 
  select(sample_ID, species, emergence_condition, emergence_date, emergence_weight, sex, starts_with("week"), length) %>% 
  ggplot() + aes(x = emergence_weight, y = week0, color = emergence_condition) + geom_point() + 
  geom_line(aes(x = emergence_weight, y = emergence_weight), color = "black") + 
  geom_text(aes(label = sample_ID), size = 2) +
  facet_wrap(vars(species)) + ylab("start weight")
error_plot_1
```

Removing observations where bees have gained weight over the course of the experiment,  as these surely represent errors in manual data entry (samples: "KB-40", "SB-166", "HC-156", "KC-151", "NC-48", "NC-187", "SC-72")
```{r}
raw_data <- raw_data %>% dplyr::filter(is.na(emergence_status) | emergence_weight <= week0)
```

Creating a subset data frame in long format that contains only samples that were weighed (tracked) weekly
```{r}
tracked_longer <- raw_data %>% dplyr::filter(batch == "weighing") %>% 
  mutate(start_weight = week0) %>% 
  pivot_longer(starts_with("week"), names_to = "week", values_to = "weight") %>% 
  mutate(rel_weight = weight / start_weight) %>% 
  mutate(week = as.numeric(str_extract(week, "\\d+")))
```


```{r, warning = F}
error_plot_2 <- tracked_longer %>% 
  dplyr::filter(!(genus == "Osmia" & is.na(sex)) & 
                  !is.na(emergence_condition)) %>% 
  ggplot() + aes(x = week, y = rel_weight) + 
  geom_text(aes(label = sample_ID), size = 2) + 
  facet_wrap(vars(species, sex, emergence_condition))
error_plot_2
```

Remove observations where obvious errors during weight loss tracking have occured ("HC-198", GB-200", "KB-65", "HC-4", "KC-188")
```{r}
raw_data <- raw_data %>% 
  dplyr::filter(!(sample_ID %in% c("HC-198", "GB-200", "KB-65", "HC-4", "KC-188")))
```

Removing SB-129 as the cocoon was completely empty with no trace of its occupant
```{r}
raw_data <- raw_data %>% dplyr::filter(sample_ID != "SB-129")
```

Removing individuals with large discrepancies between last measured weight during weight tracking and emergence weight that emerged alive
```{r, warning = F}
error_plot_3 <- raw_data %>% dplyr::filter(!is.na(week1)) %>% 
  pivot_longer(starts_with("week"), names_to = "week", values_to = "weight") %>% 
  group_by(sample_ID) %>% fill(weight) %>% ungroup() %>% dplyr::filter(week == "week21") %>% 
  ggplot() + aes(y = weight, x = emergence_weight, color = emergence_condition) + 
  geom_point() + geom_text(aes(label = sample_ID), size = 2) + 
  geom_line(aes(x = emergence_weight, y = emergence_weight), color = "black") + 
  facet_wrap(vars(species)) + ylab("Last available tracking weight")
error_plot_3
```


```{r}
clean_data <- raw_data %>% dplyr::filter(sample_ID != "HC-71")
```

```{r}
clean_data <- clean_data %>% 
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642"))
```

## Subset tables

```{r, message=F, warning=F}

# Table 1: Emerged, alive mason bees (n = 994)
# Table 2: Weight-loss tracked, emerged, alive mason bees (n = 753, long format n = 16566)
# Table 3: All mason bees, alive or dead, emerged or excised (n = 1113)
# Table 4: Summary survival stats on table 3 (n = 12)

# Table 1
complete_data <- clean_data %>% filter(emergence_status %in% c("emerged")) %>% 
  filter(emergence_condition == "alive", genus == "Osmia", !is.na(sex)) %>% 
  mutate(start_weight = week0) %>% 
  mutate(temperature = as.factor(temperature),
         species = as.factor(species),
         sample_ID = as.factor(sample_ID),
         sex = as.factor(sex),
         population = as.factor(population)) %>% 
  mutate(rel_weight_emergence = emergence_weight / start_weight) %>% 
  mutate(weight_loss_per_day = 
           100 * (1 - rel_weight_emergence) / (julian_emergence_date + 31)) %>% 
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642"))

# Table 2
weekly_tracking_data <- complete_data %>% filter(batch == "weighing") %>% 
  mutate(start_weight = week0) %>% 
  pivot_longer(starts_with("week"), names_to = "week", values_to = "weight") %>% 
  mutate(week = as.numeric(str_extract(week, "\\d+"))) %>% 
  mutate(weight = ifelse(is.na(weight), emergence_weight, weight)) %>% 
  mutate(rel_weight = weight / start_weight)

# Table 3
survival_data <- clean_data %>% 
  filter(genus == "Osmia", !is.na(emergence_condition), !is.na(sex)) %>% 
  mutate(start_weight = week0) %>% 
  mutate(temperature = as.factor(temperature),
         species = as.factor(species),
         sample_ID = as.factor(sample_ID),
         sex = as.factor(sex),
         population = as.factor(population)) %>% 
  mutate(rel_weight_emergence = emergence_weight / start_weight) %>% 
  mutate(survival = as.factor(emergence_condition))

# Table 4
survival_summary_data <- survival_data %>% group_by(temperature, species, sex) %>% 
  dplyr::summarise(survived = sum(survival == "alive"),
                   total = n(), rel_survival = survived / total) %>% ungroup() %>% 
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642")) 

```

## Models

### Emergence model
```{r, message=F, warning=F}
# Model 1: LME with with the full data set, including all samples that emerged during
# the course of the experiment and their respective weight loss relative to the 
# start of the experiment. Weekly-tracking data is not used in favor of a 
# simpler model and a bigger part of the data set.

# mod1 <- nlme::lme(julian_emergence_date ~ temperature * sex * species, 
#                       random = ~ 1|population, data = complete_data)
mod1 <- lme4::lmer(julian_emergence_date ~ temperature * sex * species + (1|population), 
                       data = complete_data)

grid <- complete_data %>% data_grid(temperature, species, sex, population) %>%
  add_predictions(mod1, "julian_emergence_date") %>%
  group_by(temperature, species, sex) %>%
  dplyr::summarise(julian_emergence_date = median(julian_emergence_date))

car::Anova(mod1, type = 2)
```

### Weight loss model
```{r, message=F, warning=F}

# Model 2: LME with with the full data set, including all samples that emerged during
# the course of the experiment and their respective weight loss relative to the 
# start of the experiment. Weekly-tracking data is not used in favor of a 
# simpler model and a bigger part of the data set.

# mod2 <- nlme::lme(rel_weight_emergence ~ temperature * species * sex, 
#                       random = ~ 1|population, 
#                       weights = varFixed(~as.numeric(temperature)),
#                       data = complete_data)
mod2 <- lme4::lmer(rel_weight_emergence ~ temperature * species * sex + (1|population), 
                         data = complete_data)

car::Anova(mod2, type = 2)

```


### GAMM weekly weight loss model
```{r}

#Model 3: Generative Additive Mixed Effect Model (GAMM) with data from
# all weekly-tracking samples and weights at weeks after hatching imputed 
# (imputed values equals values at emergence/hatching)
# Additional Info: With a GAM, week can be modeled as a smooth term (with temperature, species 
# and sex as interaction terms) such that variations of weight loss across time
# can be more accurately captured by the model

mod3 <- gamm(formula = rel_weight ~
                   s(week, k = 10, by = interaction(temperature, species, sex)) +
                   temperature * species * sex, family = "gaussian",
                 random = list(population = ~1, sample_ID = ~1),
                 data = weekly_tracking_data, method = "REML")

mod3$gam$call <- quote(gamm(formula = rel_weight ~
                                  s(week, k = 10, by = interaction(temperature, species, sex)) +
                                  temperature * species * sex, family = "gaussian",
                                random = list(population = ~1, sample_ID = ~1),
                                data = weekly_tracking_data, method = "REML"))

```

### Survival model
```{r, message=F, warning=F}
# Model 4: Generalised Linear Mixed Effect Model (GLME) on survival data set,
# containing all samples and whether or not they were alive or dead at emergence
# or at the finishing time of the experiment when all remaining individuals were excised
# from their cocoons

mod4 <- glmer(survival ~ temperature * species * sex + (1|population), 
                  family = binomial, data = survival_data)

car::Anova(mod1, type = 2)

# mod4_tmp <- emmeans::emmeans(mod4, ~ temperature | species * sex)
# contrast(mod4_tmp, interaction = "pairwise", adjust = "holm")
# 
# mod4_tmp <- emmeans::emmeans(mod4, ~ species | temperature * sex)
# contrast(mod4_tmp, interaction = "pairwise", adjust = "holm")
# 
# mod4_tmp <- emmeans::emmeans(mod4, ~ sex | species * temperature)
# contrast(mod4_tmp, interaction = "pairwise", adjust = "holm")

```

### Influence of initial body weight or body size on emergence model
```{r, message=F, warning=F}
# Model 5: LME with with the full data set, including all samples that emerged during
# the course of the experiment and their respective weight loss relative to the 
# start of the experiment. The model tests the influence of initial body weight on emergence

mod5 <- lme4::lmer(julian_emergence_date ~ temperature * sex * species * 
                     start_weight + (1|population), 
                       data = complete_data)

car::Anova(mod5, type = 2)



# mod5.1 <- lme4::lmer(julian_emergence_date ~ temperature * sex * species * 
#                      length + (1|population), 
#                        data = complete_data)
# 
# car::Anova(mod5.1, type = 2)

rsq::rsq(mod1)
rsq::rsq(mod5)
#rsq::rsq(mod5.1)
```

### Influence of starting body weight or body size on weight loss model
```{r, message=F, warning=F}
# Model 6: LME with with the full data set, including all samples that emerged during
# the course of the experiment and their respective weight loss relative to the 
# start of the experiment. The model tests the influence of initial body weight on weight loss

mod6 <- lme4::lmer(rel_weight_emergence ~ temperature * species * sex * 
                     start_weight + (1|population), 
                         data = complete_data)

car::Anova(mod6, type = 2)

# mod6.1 <- lme4::lmer(rel_weight_emergence ~ temperature * species * sex * 
#                      length + (1|population), 
#                          data = complete_data)
# 
# car::Anova(mod6.1, type = 2)

rsq::rsq(mod2)
rsq::rsq(mod6)
#rsq::rsq(mod6.1)
```


### Moderated Mediation Analysis

```{r}
# Mediation analysis with multilevel linear models to test if weight loss as a 
# mediator variable (moderated by the interaction variables species and sex) 
# is able to explain the effect of temperature on emergence timing 

lme_mod_med <- lme4::lmer(rel_weight_emergence ~ temperature * species * sex + (1|population), 
                         data = complete_data)

lme_mod_IV <- lme4::lmer(
  julian_emergence_date ~ temperature * species * sex + rel_weight_emergence * species * sex + (1|population),
  data = complete_data)
```


```{r, warning=F, message=F}
general_mediation_model <- mediation::mediate(
  lme_mod_med, lme_mod_IV, sims = 300,
  control.value = "current", treat.value = "SSP5-8.5", 
  treat = "temperature", mediator = "rel_weight_emergence")

# cornuta_mediation_model <- mediation::mediate(
#   lme_mod_med, lme_mod_IV, sims = 300, covariates = list(species = "O. cornuta"),
#   control.value = "current", treat.value = "SSP5-8.5", robustSE = TRUE, 
#   treat = "temperature", mediator = "rel_weight_emergence")
# 
# bicornis_mediation_model <- mediation::mediate(
#   lme_mod_med, lme_mod_IV, sims = 300, covariates = list(species = "O. bicornis"),
#   control.value = "current", treat.value = "SSP5-8.5", robustSE = TRUE,
#   treat = "temperature", mediator = "rel_weight_emergence")

summary(general_mediation_model)
# summary(cornuta_mediation_model)
# summary(bicornis_mediation_model)

```

## Plots

```{r, message=F}
# Plot 1
ssp_names <- c(
  normal = "current",
  plus3 = "SSP2-4.5",
  plus6 = "SSP5-8.5"
)

plot1 <- temp_logger_data %>% filter(cabinet %in% c("ref", "ref+3", "ref+6")) %>% 
  ggplot() + geom_line(aes(x = datetime, y = temp, group = cabinet), alpha = 0.5) + 
  geom_line(data = temp_logger_data %>% filter(cabinet %in% c("C", "E", "F")),
            aes(x = datetime, y = temp, color = cabinet, group = cabinet)) + 
  scale_x_datetime(name = element_blank()) + 
  facet_wrap(vars(group), nrow = 3, labeller = labeller(group = ssp_names)) + 
  scale_color_discrete(guide = "none", type = customPalette1) + 
  ylab("temperature [°C]") + 
  theme_minimal() +
  theme(panel.border = element_rect(fill = NA),
        axis.ticks = element_line(),
        plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10),
        strip.text = element_text(size = 12, face = "bold")
        )

png(file = "plots/plot1.png", width=7.5, height=5, units = "in", res = 600)
print(plot1)
dev.off()  

plot1
```


```{r, message=F}
# Plot 2.1
plot2.1 <- complete_data %>% 
  mutate(species_sex_symbolic = paste0("*", species, "* (", '<span style="font-family:Sans-Serif;font-size:14px">', sex_symbolic, '</span>', ")")) %>% 
  mutate(temperature = factor(temperature, levels = c("SSP5-8.5", "SSP2-4.5", "current"))) %>% 
  ggplot() + 
  geom_histogram(aes(x = julian_emergence_date, fill = species_sex_symbolic), binwidth = 1) + 
  scale_fill_discrete(type = customPalette2, name = NULL, 
                      guide = guide_legend(reverse = TRUE)) + 
  scale_x_continuous(name = "emergence date [Julian days]") + 
  scale_y_continuous(name = "number of emerged individuals") + 
  facet_wrap(vars(temperature), nrow = 3) + theme_minimal() +
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.5,0.25), "cm"),
      axis.text.x = element_text(size = 10),
      axis.title.y = element_text(size = 10, face = "bold"),
      axis.text.y = element_text(size = 10),
      axis.title.x = element_text(size = 10, face = "bold"),
      strip.text = element_text(size = 12, face = "bold"),
      legend.position = "bottom",
      legend.text = ggtext::element_markdown(size = 12),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )


png(file = "plots/plot2.1.png", width=7.5, height=5, units = "in", res = 600)
print(plot2.1)
dev.off()  
```

```{r, warning = F, message=F}
#Plot 2.2
emm_options(parens = "a^")
mod_tmp <- emmeans::emmeans(mod1, ~ temperature | species * sex)
emergence_temp_focused_res <- contrast(mod_tmp, interaction = "pairwise", adjust = "holm") %>% 
  as_tibble() %>% separate_wider_delim(ends_with("pairwise"), delim = " - ", 
                     names = c("group1", "group2")) %>% 
  dplyr::select(group1, group2, p.value, everything()) %>% 
  mutate(p.signif.label = symnum(p.value, corr = FALSE, na = FALSE, 
                         cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                         symbols = c("****", "***", "**", "*", "ns"))) %>% 
  mutate(p.val.label = ifelse(p.value > 0.01, paste0("Padj = ", round(p.value, 2)),
                              "Padj < 0.01")) %>%
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642")) %>% 
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")"))
  
plot2.2 <- complete_data %>%
  mutate(species_sex_symbolic = paste0("*", species, "* (", '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">', sex_symbolic, '</span>', ")")) %>% 
  ggplot(aes(y = julian_emergence_date, x = temperature)) +
  geom_boxplot() + #geom_point(data = grid, colour = "red") +
  facet_wrap(vars(species_sex_symbolic), ncol = 2, nrow = 2) + 
  ylab("emergence date [Julian days]") + 
  ylim(c(25, 150)) +
  ggpubr::stat_pvalue_manual(
    emergence_temp_focused_res, 
    label = "p.signif.label", y.position = c(130, 150, 140)) + 
  theme_minimal() +
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      panel.grid.major.x = element_blank(),
      axis.text.x = element_text(size = 10),
      axis.title.x = element_blank(),
      axis.text.x.bottom = element_text(size = 10, face = "bold", color = "black"),
      axis.title.y = element_text(size = 10, face = "bold"),
      axis.text.y = element_text(size = 10),
      strip.text = ggtext::element_markdown(size = 12, face = "bold"),
      legend.position = "bottom"
      )

png(file = "plots/plot2.2.png", width=7.5, height=5, units = "in", res = 600)
print(plot2.2)
dev.off()  

```

```{r, warning = F, message=F}
# Combined Plot 2 / Emergence
combined_plot2 <- plot2.1 / plot2.2 + 
  patchwork::plot_annotation(tag_levels = list(c("(a)", "(b)")))

png(file = "plots/plot2_combined.png", width=7.5, height=10, units = "in", res = 600)
print(combined_plot2)
dev.off()  

combined_plot2
```


```{r, warning = F, message=F}

# Plot 3.1
emmeans <- emmeans(mod3$gam, c("week", "temperature", "species", "sex"),
                   cov.reduce = F) %>% as_tibble() %>% 
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642")) %>% 
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")"))

plot3.1 <- weekly_tracking_data %>% mutate(rel_weight = 100 * (1 - rel_weight)) %>% 
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">', 
    sex_symbolic, '</span>', ")")) %>% 
  summarySE(measurevar = "rel_weight", 
            groupvars = c("week", "temperature", "species_sex_symbolic"), 
            conf.interval = 0.95, na.rm = F) %>% 
  ggplot() + geom_point(aes(x = week, y = rel_weight, color = temperature)) + 
  geom_line(data = emmeans, aes(x = week, y = 100 * (1 - emmean), 
                                color = temperature)) + 
  facet_wrap(vars(species_sex_symbolic), 
             labeller = label_wrap_gen(multi_line = F), ncol = 4) + 
  ylab("cumulative weight loss [%]") + 
  xlab("experimental time [weeks]") +
  scale_color_manual(values = customPalette1, 
                     guide = guide_legend(title = element_blank()),
                     labels = c("current", "SSP2-4.5", "SSP5-8.5")) + 
  geom_line(data = emmeans, aes(x = week, y = 100 * (1 - lower.CL), group = temperature), lty = 2) +
  geom_line(data = emmeans, aes(x = week, y = 100 * (1 - upper.CL), group = temperature), lty = 2) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.5,0.25), "cm"),
      axis.text.x = element_text(size = 10),
      axis.title.y = element_text(size = 10, face = "bold"),
      axis.text.y = element_text(size = 10),
      axis.title.x = element_text(size = 10, face = "bold"),
      strip.text = element_markdown(size = 12, face = "bold"),
      legend.position = "bottom",
      legend.title = element_blank(),
      legend.text = element_text(size = 12),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )

png(file = "plots/plot3.1.png", width=7.5, height=5, units = "in", res = 600)
print(plot3.1)
dev.off()  
```

```{r, warning = F, message=F}

# Plot 3.2
emm_options(parens = "a^")
mod_tmp <- emmeans::emmeans(mod2, ~ temperature | species * sex)
temp_focused_res <- contrast(mod_tmp, interaction = "pairwise", adjust = "holm") %>% 
  as_tibble() %>% separate_wider_delim(ends_with("pairwise"), delim = " - ", 
                     names = c("group1", "group2")) %>% 
  dplyr::select(group1, group2, p.value, everything()) %>% 
  mutate(p.signif.label = symnum(p.value, corr = FALSE, na = FALSE, 
                         cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                         symbols = c("****", "***", "**", "*", "ns"))) %>% 
  mutate(p.val.label = ifelse(p.value > 0.01, paste0("Padj = ", round(p.value, 2)),
                              "Padj < 0.01")) %>%
  mutate(sex_symbolic = ifelse(sex == "female", "\U2640", "\U2642")) %>% 
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")"))

plot3.2 <- complete_data %>%
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% 
  ggplot(aes(y = (1 - rel_weight_emergence) * 100, x = temperature)) +
  geom_boxplot() + facet_wrap(vars(species_sex_symbolic), 
                              labeller = label_wrap_gen(multi_line = FALSE)) + 
  ylab("cumulative weight loss at emergence [%]") + 
  ylim(c(3, 29)) + 
  ggpubr::stat_pvalue_manual(temp_focused_res, label = "p.signif.label", 
                             y.position = c(24, 28, 26)) + 
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.x = element_text(size = 10, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 10, face = "bold"),
      axis.text.y = element_text(size = 10),
      axis.title.x = element_blank(),
      strip.text = element_markdown(size = 12, face = "bold"),
      legend.position = "bottom",
      legend.title = element_blank(),
      legend.text = element_text(size = 10),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )

png(file = "plots/plot3.2.png", width=7.5, height=5, units = "in", res = 600)
print(plot3.2)
dev.off()  
```

```{r, warning = F, message=F}

# Combined Plot 3 / Weight loss
combined_plot3 <- plot3.1 / plot3.2 + 
  patchwork::plot_annotation(tag_levels = list(c("(a)", "(b)")))

png(file = "plots/plot3_combined.png", width=7.5, height=10, units = "in", res = 600)
print(combined_plot3)
dev.off()  

combined_plot3
```

```{r, warning = F, message=F}

# Plot 4 / Survival

plot4 <- survival_summary_data %>% 
  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% 
  ggplot() + 
  geom_col(aes(y = temperature, x = (1 - rel_survival) * 100, 
           group = species_sex_symbolic, 
           fill = species_sex_symbolic)) + 
  facet_wrap(vars(fct_relevel(species_sex_symbolic, rev(unique(species_sex_symbolic)))), nrow = 4) + 
  xlab("mortality rate [%]") +
  scale_fill_discrete(type = customPalette2, name = NULL, 
                      guide = guide_legend(reverse = T)) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.y = element_text(size = 10, colour = "black", face = "bold"),
      axis.title.x = element_text(size = 10, face = "bold"),
      axis.text.x = element_text(size = 10),
      axis.title.y = element_blank(),
      strip.text = element_blank(),
      legend.position = "bottom",
      legend.title = element_blank(),
      legend.text = element_markdown(size = 12),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )

png(file = "plots/plot4.png", width=7.5, height=7.5, units = "in", res = 600)
print(plot4)
dev.off()  

plot4
```
## Supplemental plots

```{r, warning = F, message=F}


# Supplemental plot 1.1
supp_plot1.1 <- complete_data %>%  mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% 
  ggplot(aes(y = (weight_loss_per_day), x = temperature, 
             color = species_sex_symbolic)) +
  geom_boxplot() +
  facet_wrap(vars(species)) + ylab("rate of weight loss [%/d]") +
  scale_fill_discrete(type = customPalette2, name = NULL, 
                      guide = guide_legend(reverse = T)) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.y = element_text(size = 10, colour = "black"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(size = 10, face = "bold"),
      axis.title.y = element_markdown(size = 10, face = "bold"),
      strip.text = element_blank(),
      legend.position = "none"
      )

# Supplemental plot 1.2 
supp_plot1.2 <- complete_data %>% mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% 
  ggplot(aes(y = (weight_loss_per_day), x = temperature, 
             color = species_sex_symbolic)) +
  geom_boxplot() +
  facet_wrap(vars(sex)) + ylab("rate of weight loss [%/d]") +
  scale_fill_discrete(type = customPalette2, name = NULL, 
                      guide = guide_legend(reverse = T)) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.y = element_text(size = 10, colour = "black"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(size = 10, face = "bold"),
      axis.title.y = element_markdown(size = 10, face = "bold"),
      strip.text = element_blank(),
      legend.position = "bottom",
      legend.title = element_blank(),
      legend.text = element_markdown(size = 12, face = "bold"),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )

# Combined Supplemental Plot 1 / Species and sex differences in rate of weight loss
combined_supp_plot1 <- supp_plot1.1 / supp_plot1.2 + 
  patchwork::plot_annotation(tag_levels = list(c("(a)", "(b)")))

png(file = "plots/supp_plot1_combined.png", width=7.5, height=10, units = "in", res = 600)
print(combined_supp_plot1)
dev.off()  

combined_supp_plot1 
```


```{r, warning = F, message=F}

# Supplemental Plot 2.1
supp_plot2.1 <- complete_data %>% mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% ggplot() + 
  aes(x = start_weight, y = julian_emergence_date, color = temperature) + 
  geom_point() + facet_wrap(vars(species_sex_symbolic), ncol = 2) + 
  geom_smooth(method = "lm") + 
  ylab("emergence date [Julian days]") + xlab("initial body weight [mg]") + 
  scale_color_discrete(type = customPalette1, name = NULL) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.y = element_text(size = 10, colour = "black"),
      axis.title.x = element_text(size = 10, face = "bold"),
      axis.text.x = element_text(size = 10),
      axis.title.y = element_markdown(size = 10, face = "bold"),
      strip.text = element_markdown(size = 12, face = "bold"),
      legend.position = "none"
      )

# Supplemental Plot 2.2
supp_plot2.2 <- complete_data %>% mutate(species_sex_symbolic = paste0(
    "*", species, "* (", 
    '<span style="font-family:Sans-Serif;font-size:18px;font-weigth:900">',
    sex_symbolic, '</span>', ")")) %>% ggplot() + 
  aes(x = start_weight, y = 100 * (1 - rel_weight_emergence), color = temperature) + 
  geom_point() + facet_wrap(vars(species_sex_symbolic), ncol = 2) + 
  geom_smooth(method = "lm") + 
  ylab("cumulative weight loss at emergence [%]") + xlab("initial body weight [mg]") +
  scale_color_discrete(type = customPalette1, name = NULL) +
  theme_minimal() + 
  theme(panel.border = element_rect(fill = NA),
      axis.ticks = element_line(),
      plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
      axis.text.y = element_text(size = 10, colour = "black"),
      axis.title.x = element_text(size = 10, face = "bold"),
      axis.text.x = element_text(size = 10),
      axis.title.y = element_markdown(size = 10, face = "bold"),
      strip.text = element_markdown(size = 12, face = "bold"),
      legend.position = "bottom",
      legend.title = element_blank(),
      legend.text = element_markdown(size = 12, face = "bold"),
      legend.box.background = element_rect(
        fill = "white", color = "black", linewidth = 0.2),
      legend.key.height = unit(0.25, "cm")
      )



# Combined Supplemental Plot 2 / Effect of body condition on weight loss and emergence
combined_supp_plot2 <- supp_plot2.1 / supp_plot2.2 + 
  patchwork::plot_annotation(tag_levels = list(c("(a)", "(b)")))

png(file = "plots/supp_plot2_combined.png", width=7.5, height=10, units = "in", res = 600)
print(combined_supp_plot2)
dev.off()  

combined_supp_plot_2
```

